Toward theories of deliberated preferences

### 2020-08-18 simple.tex
Negation is now optional.

A normative theory also defines an involution operator $¬$ on $\allprops$, thus a function $¬: \allprops → \allprops$ satisfying $\forall \prop \in \allprops: ¬¬\prop = \prop$.
(The symbol $¬$ is also used in this article to negate classical mathematical propositions; this should create no confusion.)

A normative theory is a tuple $(\allprops, ¬, \allargs, I, {\allleadsto})$ 
%with $\allprops$ an agenda, $¬$ a negation operator on $\allprops$, $\allargs$ a set of arguments, $I$ a set of individuals, and ${\allleadsto}$ an observation protocol, 
satisfying the constraints described here above.
%where $\allprops = \allprops × \set{\mathit{poss}, \mathit{sure}}$.

@@

Given $i \in I, \prop \in \allprops, \hist \in \allhist$, say that $\hist$ leads strongly to $\prop$, $\hist \ileadstost \prop$, iff $\hist \ileadsto \prop \land \hist \nileadsto ¬\prop$.
(The visual proximity of the symbols $\ileadsto$ and $\ileadstost$ creates a small risk of confusion, but its usage seems justified by the fact that $\ileadsto$ is not used in the rest of this article, except in the proof of \cref{th:protcoh}.)

@@

\begin{remark}
	I’d rather drop the negation and observe that if the protocol is defined so that $\hist \ileadsto \prop_1 ⇒ \hist \nileadsto \prop_2$, then $\prop_1 \in \iprops ⇒ \prop_2 \notin \iprops$. Observe that this is always possible. The definitions about completeness should use a negation operator in supplement to the normative theory tuple.
\end{remark}

\subsection{Classify propositions}
\begin{axiom}[Normative adequacy]
	\label{ax:norm}
	$\forall i \in I, \prop \in \allprops: 
		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \prop) \land ¬(\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\prop)] ⇒ \prop \in \iprops \land ¬\prop \notin \iprops.$
\end{axiom}

\Cref{ax:norm} is actually equivalent to the following property.
\begin{property}[Simple normative adequacy]
	\label{ax:snorm}
	$\forall i \in I, \prop \in \allprops: 
		[\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ \prop \in \iprops \land ¬\prop \notin \iprops.$
\end{property}

To see why this hold, consider the following definition and proposition.
\begin{definition}[Protocol coherence]
	\label{def:protcoh}
	$\forall i \in I, \prop \in \allprops$:
	\begin{equation}
		[\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost ¬\prop].
	\end{equation}
\end{definition}
\begin{proposition}
	\label{th:protcoh}
	Any normative theory satisfies Protocol coherence.
\end{proposition}
\begin{proof}
	Protocol coherence is satisfied by definition of $\ileadstost$. Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost \prop$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto ¬\prop$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost ¬\prop$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto ¬\prop$, and thus in particular, that $(\ar', \ar) \ileadsto ¬\prop$.
\end{proof}

That \cref{ax:norm} is equivalent to \cref{ax:snorm} immediately follows from \cref{th:protcoh}.
\begin{proposition}
	\label{th:normeqsnorm}
	Any normative theory satisfies Normative adequacy iff it satisfies simple normative adequacy.
\end{proposition}

To further analyze this and related matters, given a normative theory and $i \in I$, say that a proposition $\prop \in \allprops$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop$.
The $i$-decidable propositions are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
The next property ensures an unambiguous interpretation of the content of $\iprops$ for all $i$-decidable propositions. In this definition, $\oplus$ denotes the exclusive disjunction; thus $\prop \in \iprops \oplus ¬\prop \in \iprops$ is equivalent to: $\prop \in \iprops ⇔ ¬\prop \notin \iprops$. It can be seen to hold by using \cref{th:normeqsnorm}.

\begin{property}[Restricted interpretability]
	\label{def:restrinterpr}
	$\forall i \in I, \prop \in \allprops: [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop] ⇒ [\prop \in \iprops \oplus ¬\prop \in \iprops]$.
\end{property}

\subsection{Non-completeness}
\label{sec:incompl}
\begin{definition}[Theory completeness]
	$\forall \prop \in \allprops: [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] \lor [\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\prop]$.
\end{definition}
\begin{definition}[Unrestricted interpretability]
	$\forall \prop \in \allprops: \prop \in \iprops \oplus ¬\prop \in \iprops$.
\end{definition}
\begin{definition}[Deliberation completeness]
	$\forall \prop \in \allprops: \prop \in \iprops \lor ¬\prop \in \iprops$.
\end{definition}
The following proposition directly follows from the definitions, together with \cref{th:protcoh}.
\begin{proposition}
	1) Under Normative adequacy, Theory completeness implies Deliberation completeness. 2) Unrestricted interpretability implies Deliberation completeness.
\end{proposition}
Theories as defined here do not mandate Theory completeness. This is good for two reasons. First, even the weaker Deliberation completeness can be considered too strong. Second, it is dubious that, for non trivial decision problems, theories can be found for which both Normative adequacy is normatively compelling and Theory completeness holds.

@@

An example permits to ensure that the constraint of finite depth does not mandate finiteness of the relations $\gbeats$ or $\dbeats$.
\begin{proposition}[Possibility of infinite relations]
	An empirical theory may involve infinite relations $\gbeats$ and $\dbeats$.
\end{proposition}
\begin{proof}
	Consider an agenda containing two propositions, $\allprops = \set{\prop, ¬\prop}$, an infinite set of arguments $\allargs = \set{\ar_k \suchthat k \in \N}$ with $\forall j, k \in \N: \ar_j ≠ \ar_k$, and consider any set of individuals $I$ and observation protocol $\allleadsto$. 
	Define $2\N^* = \set{k \suchthat k / 2 \in \N^*}$ as the set of non-zero even integers.
	Define ${\gleadsto} = \set{(\ar_0, \prop)}$.
	Define ${\gbeats} = \set{(\ar_{k - 1}, \ar_0) \suchthat k \in 2\N^*}$ so that all odd numbered arguments are planned attacks against $\ar_0$. 
	Consider an infinite set of fragments $\alldargs = \set{\ard[k] \suchthat k \in 2\N^*}$ with $\forall j, k \in 2\N^*: \ard[j] ≠ \ard[k]$ so that fragments correspond to non-zero even integers, and define ${\dbeats} = \set{(\ard[k], \ar_{k - 1}) \suchthat k \in 2\N^*}$ so that each (even numbered) defense fragment attacks exactly one (odd numbered) planned attacker of $\ar_0$. 
	Given any coalition of fragments $\dargs$ defending $\ar_0$, consider the set of indices corresponding to the fragments in the coalition, $K_{\dargs} = \set{k \in 2\N^* \suchthat \exists \ard[k] \in \dargs}$; 
	define $j_{\dargs} = \sum_{k \in K_{\dargs}}$ as the sum of these indices;
	and define $\ar_0 + \dargs = \ar_{j_{\dargs}}$. 
%	$\ard[k] \in \alldargs$, define $\ar_0 + \set{\ard[k]} = \ar_k$. 
	Consider an empirical theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ for the normative theory $(\allprops, ¬, \allargs, I, {\allleadsto})$. That this is indeed a legal empirical theory can be confirmed by checking that all constraints are satisfied, in particular, $(\dfp)^2(\gleadstoinv(\allprops)) = \dfp(\dfp(\ar_0)) = \dfp(\set{\ar_k \suchthat k \in 2\N^*}) = \emptyset$ because there is no planned attack against any argument in $\set{\ar_k \suchthat k \in 2\N^*}$. This theory involves infinite relations $\gbeats$ and $\dbeats$.
\end{proof}

@@

\begin{definition}[Validity]
	An empirical theory is \emph{valid} iff $\forall i \in I, \prop \in \gpropse: [\prop \in \iprops \land ¬\prop \notin \iprops]$.
\end{definition}

@@

\begin{theorem}
	A normatively adequate and convincing empirical theory is valid.
\end{theorem}
\begin{proof}
	Given any $i \in I$ and $\prop \in \gpropse$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \prop$; the conclusion then follows thanks to simple normative adequacy (that \cref{th:normeqsnorm} shows to be equivalent to normative adequacy).

@@

\subsection{Effectively comparing models}
Given $\prop \in \allprops$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $\prop$ iff $\prop \in \gpropse[\gamma] \land ¬\prop \in \gpropse[\delta]$. Say that they are incompatible iff there is at least one $\prop \in \allprops$ that they disagree about.

Given $\prop \in \allprops$, $\hist \in \allhist$ and $\ar_\gamma \in \gargs$, say that $(\hist, \ar_\gamma)$ challenges $\prop$ iff $\hist \nileadstost \prop$ and $\ar_\gamma \in \histend$.
Given $\prop \in \allprops, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/¬\prop$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \prop)$ or $(\hist, \ar_\delta)$ challenges $(\delta, ¬\prop)$.

\begin{lemma}
	\label{th:endchal}
	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$, $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/¬\prop$-challenge.
\end{lemma}
\begin{proof}
	Either $\hist \nileadstost \prop$, and $(\hist, \ar_\gamma)$ challenges $\prop$, or $\hist \ileadstost \prop$, hence, by \cref{th:protcoh}, $\hist \nileadstost ¬\prop$, and $(\hist, \ar_\delta)$ challenges $¬\prop$. 
\end{proof}

\begin{lemma}
	\label{th:nextchal}
	Given $(\hist, \ar_\gamma)$ challenging $\prop$, with $\ar_\gamma \in \gargs \cap (\dfp)^k(\gleadstoinv(\prop))$, and $\ar_\delta \in \gargsdelta$: either $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $\prop/¬\prop$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\prop))$.
\end{lemma}
\begin{proof}
	If $\ar_\gamma$ does not $i$-defend $\prop$, then $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, which ends the proof. 
	Thus, assume that $\ar_\gamma$ $i$-defends $\prop$.

@@

	Given $k_\alpha, k_\beta \in \N, \hist \in \allhist, \ar_\alpha \in \gargsalpha, \ar_\beta \in \gargsbeta$, 
	say that 
	$(\hist, \ar_\alpha, \ar_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta)$ iff 
	$(\hist, \ar_\alpha, \ar_\beta)$ is a $\prop/¬\prop$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\prop))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](¬\prop))$.

	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[\beta] ¬\prop$. Observe that $\ar_{-1} \in \gargsbeta \cap (\dfp[\beta])^0(\gleadstoinv[\beta](¬\prop))$. Test whether $(\ar_{-1}) \nileadstost \prop$. If so, $(i, \prop, (\ar_{-1}), \ar_{-1})$ falsifies $\beta$, which ends the procedure. 
	Thus, assume that $(\ar_{-1}) \ileadstost \prop$.

	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[\alpha] \prop$. Observe that $\ar_0 \in \gargsalpha \cap (\dfp[\alpha])^0(\gleadstoinv[\alpha](\prop))$.  Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadstost \prop$. By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $\prop/¬\prop$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.

	Suffices now to apply \cref{th:nextchal} repetitively, until finding a falsification instance of $\alpha$ or $\beta$. This is because, given a challenge $(\hist, \ar_\alpha, \ar_\beta)$ of complexity $(k_\alpha, k_\beta)$, \cref{th:nextchal} applies, yielding either a falsification instance, or a new challenge of higher complexity. 
Indeed, if $(\hist, \ar_\alpha)$ challenges $\prop$, apply \cref{th:nextchal} with $\alpha$ for $\gamma$, $\beta$ for $\delta$, and obtain either that $\hist$ falsifies $\alpha$, or a new tuple $(\histp, \ar'_\alpha, \ar_\beta)$ that is a challenge of complexity $(k_\alpha + 1, k_\beta)$.
And if $(\hist, \ar_\beta)$ challenges $¬\prop$, apply \cref{th:nextchal} with $¬\prop$ for $\prop$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.

	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\prop)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](¬\prop)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
\end{procedure}

>>>>

A normative theory is a tuple $(\allprops, \allargs, I, {\allleadsto})$ 
satisfying the constraints described here above.

@@

@@

\subsection{Coherence}
\begin{axiom}[Normative adequacy]
	\label{ax:norm}
	$\forall i \in I, \prop \in \allprops: 
		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \prop)] ⇒ \prop \in \iprops.$
\end{axiom}

A relation $n \subseteq \allprops × \allprops$ is said to be an incompatibility relation iff $\forall \hist \in \allhist, (\prop, \propbar) \in n: \hist \ileadsto \prop ⇒ \hist \nileadsto \propbar$. Two propositions $\prop, \prop' \in \allprops$ are said to be incompatible iff $(\prop, \prop') \in n$. Such a pair will generally denoted by $(\prop, \propbar)$.
(This article does not use the overline to denote set complementarity, thus this notation should create no confusion.)

It is desirable to ensure that this axiom cannot lead to incompatible propositions being considered deliberated. Consider the following proposition.
\begin{proposition}[Protocol coherence]
	\label{th:protcoh}
	Given any normative theory and incompatibility relation $n$,
	$\forall i \in I, (\prop, \propbar) \in n$:
	\begin{equation}
		[\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost \propbar].
	\end{equation}
\end{proposition}
\begin{proof}
	If for some $\ar \in \allargs$, $\ar \ileadstost \prop$, then by definition of $\ileadstost$, $\forall \ar_1 \in \allargs: (\ar_1, \ar) \ileadsto \prop$, thus by definition of $n$, $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto \propbar$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost \propbar$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto \propbar$, and thus in particular, that $(\ar', \ar) \ileadsto \propbar$.
\end{proof}

To further analyze this and related matters, consider defined a negation operator $¬$ on $\allprops$. $¬$ is a negation operator iff it is an involution operator (thus a function $¬: \allprops → \allprops$ satisfying $\forall \prop \in \allprops: ¬¬\prop = \prop$) and furthermore satisfying, $\forall \phi \in \allprops: \hist \ileadsto \prop ⇒ \hist \nileadsto ¬\prop$.
Given any $i \in I$, say that a proposition $\prop \in \allprops$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost \propbar$.
The $i$-decidable propositions are those on which the normative theory permits to take a position. 
%It will generally be unknown in practical applications, and may be empty.
The next proposition ensures an unambiguous interpretation of the content of $\iprops$ for all $i$-decidable propositions. The symbol $\oplus$ denotes the exclusive disjunction; thus $\prop \in \iprops \oplus ¬\prop \in \iprops$ is equivalent to: $\prop \in \iprops ⇔ ¬\prop \notin \iprops$. It can be seen to hold by using \cref{th:protcoh}.

\begin{proposition}[Restricted interpretability]
	\label{th:restrinterpr}
	Any normative theory with a negation operator $¬$ satisfy,
	$\forall i \in I, \prop \in \allprops: [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop \lor \ar \ileadstost ¬\prop] ⇒ [\prop \in \iprops \oplus ¬\prop \in \iprops]$.
\end{proposition}

This interpretability is however restricted to the $i$-decidable propositions. The following definitions and propositions (assuming a normative theory and a negation operator $¬$ defined) argue that going further is not desirable.

\begin{definition}[Theory completeness]
	$\forall \prop \in \allprops: [\exists \ar \in \allargs \suchthat \ar \ileadstost \prop] \lor [\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\prop]$.
\end{definition}
\begin{definition}[Unrestricted interpretability]
	$\forall \prop \in \allprops: \prop \in \iprops \oplus ¬\prop \in \iprops$.
\end{definition}
\begin{definition}[Deliberation completeness]
	$\forall \prop \in \allprops: \prop \in \iprops \lor ¬\prop \in \iprops$.
\end{definition}
The following proposition directly follows from the definitions, together with \cref{th:protcoh}.
\begin{proposition}
	1) Under Normative adequacy, Theory completeness implies Deliberation completeness. 2) Unrestricted interpretability implies Deliberation completeness.
\end{proposition}
Theories as defined here do not mandate Theory completeness. This is good for two reasons. First, even the weaker Deliberation completeness can be considered too strong. Second, it is dubious that, for non trivial decision problems, theories can be found for which both Normative adequacy is normatively compelling and Theory completeness holds.

@@

An example permits to ensure that the constraint of finite depth does not mandate finiteness of the relations $\gbeats$ or $\dbeats$.
\begin{proposition}[Possibility of infinite relations]
	An empirical theory may involve infinite relations $\gbeats$ and $\dbeats$.
\end{proposition}
\begin{proof}
	Consider an agenda $\allprops = \set{\prop}$ containing a single proposition, an infinite set of arguments $\allargs = \set{\ar_k \suchthat k \in \N}$ with $\forall j, k \in \N: \ar_j ≠ \ar_k$, and consider any set of individuals $I$ and observation protocol $\allleadsto$. 
	Define $2\N^* = \set{k \in \N^* \suchthat k / 2 \in \N^*}$ as the set of non-zero even integers.
	Define ${\gleadsto} = \set{(\ar_0, \prop)}$.
	Define ${\gbeats} = \set{(\ar_{k - 1}, \ar_0) \suchthat k \in 2\N^*}$ so that all odd numbered arguments are planned attacks against $\ar_0$. 
	Consider an infinite set of fragments $\alldargs = \set{\ard[k] \suchthat k \in 2\N^*}$ with $\forall j, k \in 2\N^*: \ard[j] ≠ \ard[k]$ so that fragments correspond to non-zero even integers, and define ${\dbeats} = \set{(\ard[k], \ar_{k - 1}) \suchthat k \in 2\N^*}$ so that each (even numbered) defense fragment attacks exactly one (odd numbered) planned attacker of $\ar_0$. 
	Given any coalition of fragments $\dargs$ defending $\ar_0$, consider the set of indices corresponding to the fragments in the coalition, $K_{\dargs} = \set{k \in 2\N^* \suchthat \exists \ard[k] \in \dargs}$; 
	define $j_{\dargs} = \sum_{k \in K_{\dargs}}$ as the sum of these indices;
	and define $\ar_0 + \dargs = \ar_{j_{\dargs}}$. 
%	$\ard[k] \in \alldargs$, define $\ar_0 + \set{\ard[k]} = \ar_k$. 
	Consider an empirical theory $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$ for the normative theory $(\allprops, \allargs, I, {\allleadsto})$. That this is indeed a legal empirical theory can be confirmed by checking that all constraints are satisfied, in particular, $(\dfp)^2(\gleadstoinv(\allprops)) = \dfp(\dfp(\ar_0)) = \dfp(\set{\ar_k \suchthat k \in 2\N^*}) = \emptyset$ because there is no planned attack against any argument in $\set{\ar_k \suchthat k \in 2\N^*}$. This theory involves infinite relations $\gbeats$ and $\dbeats$.
\end{proof}

@@

\begin{definition}[Validity]
	An empirical theory is \emph{valid} iff $\forall i \in I, \prop \in \gpropse: \prop \in \iprops$.
\end{definition}

@@

\begin{theorem}
	A normatively adequate and convincing empirical theory is valid.
\end{theorem}
\begin{proof}
	Given any $i \in I$ and $\prop \in \gpropse$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \prop$; the conclusion then follows thanks to normative adequacy.

@@

\subsection{Effectively comparing models}
Given $\prop \in \allprops$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory with an incompatibility relation $n$, say that they disagree about $(\prop, \propbar) \in n$ iff $\prop \in \gpropse[\gamma] \land \propbar \in \gpropse[\delta]$. Say that they are incompatible iff there is at least one pair $(\prop, \propbar) \in \allprops$ that they disagree about.

Given $\prop \in \allprops$, $\hist \in \allhist$ and $\ar_\gamma \in \gargs$, say that $(\hist, \ar_\gamma)$ challenges $\prop$ iff $\hist \nileadstost \prop$ and $\ar_\gamma \in \histend$.
Given $\prop \in \allprops, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \prop)$ or $(\hist, \ar_\delta)$ challenges $(\delta, \propbar)$.

\begin{lemma}
	\label{th:endchal}
	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$, $(\hist, \ar_\gamma, \ar_\delta)$ is a $\prop/\propbar$-challenge.
\end{lemma}
\begin{proof}
	Either $\hist \nileadstost \prop$, and $(\hist, \ar_\gamma)$ challenges $\prop$, or $\hist \ileadstost \prop$, hence, by \cref{th:protcoh}, $\hist \nileadstost \propbar$, and $(\hist, \ar_\delta)$ challenges $\propbar$. 
\end{proof}

\begin{lemma}
	\label{th:nextchal}
	Given $(\hist, \ar_\gamma)$ challenging $\prop$, with $\ar_\gamma \in \gargs \cap (\dfp)^k(\gleadstoinv(\prop))$, and $\ar_\delta \in \gargsdelta$: either $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $\prop/\propbar$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\prop))$.
\end{lemma}
\begin{proof}
	If $\ar_\gamma$ does not $i$-defend $\prop$, then $(i, \prop, \hist, \ar_\gamma)$ falsifies $\gamma$, which ends the proof. 
	Thus, assume that $\ar_\gamma$ $i$-defends $\prop$.

@@

	Given $k_\alpha, k_\beta \in \N, \hist \in \allhist, \ar_\alpha \in \gargsalpha, \ar_\beta \in \gargsbeta$, 
	say that 
	$(\hist, \ar_\alpha, \ar_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta)$ iff 
	$(\hist, \ar_\alpha, \ar_\beta)$ is a $\prop/\propbar$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\prop))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](\propbar))$.

	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[\beta] \propbar$. Observe that $\ar_{-1} \in \gargsbeta \cap (\dfp[\beta])^0(\gleadstoinv[\beta](\propbar))$. Test whether $(\ar_{-1}) \nileadstost \prop$. If so, $(i, \prop, (\ar_{-1}), \ar_{-1})$ falsifies $\beta$, which ends the procedure. 
	Thus, assume that $(\ar_{-1}) \ileadstost \prop$.

	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[\alpha] \prop$. Observe that $\ar_0 \in \gargsalpha \cap (\dfp[\alpha])^0(\gleadstoinv[\alpha](\prop))$.  Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadstost \prop$. By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $\prop/\propbar$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.

	Suffices now to apply \cref{th:nextchal} repetitively, until finding a falsification instance of $\alpha$ or $\beta$. This is because, given a challenge $(\hist, \ar_\alpha, \ar_\beta)$ of complexity $(k_\alpha, k_\beta)$, \cref{th:nextchal} applies, yielding either a falsification instance, or a new challenge of higher complexity. 
Indeed, if $(\hist, \ar_\alpha)$ challenges $\prop$, apply \cref{th:nextchal} with $\alpha$ for $\gamma$, $\beta$ for $\delta$, and obtain either that $\hist$ falsifies $\alpha$, or a new tuple $(\histp, \ar'_\alpha, \ar_\beta)$ that is a challenge of complexity $(k_\alpha + 1, k_\beta)$.
And if $(\hist, \ar_\beta)$ challenges $\propbar$, apply \cref{th:nextchal} with $\propbar$ for $\prop$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.

	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\prop)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](\propbar)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
\end{procedure}
